Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-26 paper/sw-contract.tex
Add test output figure and fix typo.

The assumption on \lineref{line:sw-assume-3} constrains when a request can arrive by reasoning about the \emph{state} of the contract defined be the associated streams.
When writing assumptions and guarantees, it is important to differentiate pre-state, before a contract updates its state, and post-state, after a contract updates its state, in response to the current input.
The \texttt{pre} naturally makes that distinction.
In general, assumptions regarding state should be evaluated in the pre-state of the component with the current inputs, and guarantees regarding state should be evaluated on the post-state of the component given the current inputs.
Additionally, guarantees should use \texttt{pre} anytime they need to reason about the current state relative to the previous state.

>>>>

The assumption on \lineref{line:sw-assume-3} constrains when a request can arrive by reasoning about the \emph{state} of the contract.
When writing assumptions and guarantees, it is important to differentiate pre-state, before a contract updates its state, and post-state, after a contract updates its state, in response to the current input.
The \texttt{pre} naturally makes that distinction by looking back one step in the stream.
In general, assumptions regarding state should be evaluated in the pre-state of the component with the current inputs, and guarantees regarding state should be evaluated on the post-state of the component given the current inputs.
Additionally, guarantees should use \texttt{pre} anytime they need to reason about the current state relative to the previous state.

### 2022-03-26 paper/testing.tex
Corrected spelling of Liskov, a few more reference cleanups
Add test output figure and fix typo.

Unit tests are created in AGREE by writing a system specification that assumes the test input and then guarantees the test output.
The system is then implemented with the component under test and its specification.
The AGREE analysis then proves if the component guarantees, given the test inputs, are strong enough to prove the guaranteed test outputs.
Here the system assumptions strengthen the component assumptions to a single input, and the system guarantees weaken, or leave unchanged, the component output for that test input, depending on the goal of the test.
AGREE proves the component implements the test, and the Liskhov substitution principle holds.

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{c}
    \scalebox{0.62}{\usebox{\tst}} \\
    \end{tabular}
  \end{center}
  \caption{AGREE Unit test for high-assurance monitor.}
  \label{fig:test}
\end{figure}

\figref{fig:test} is a unit test for the high-assurance monitor in \figref{fig:hardened}.
The test checks if the monitor output coincides with the response that comes one step after the request.
It also checks that the alarm does not fire.
\lineref{line:tst-index} creates an index to use to create the test input.
\lineref{line:tst-assume-1} defines when the response appears relative to the index.
\lineref{line:tst-assume-2} defines the request behavior.
\linesref{line:tst-guarantee-1}{line:tst-guarantee-2} define the expected test output.
The test additionally proves that nothing happens after the initial test input and output (e.g., no more input is provided and no more output is generated).
AGREE proves the test correct.
\linesref{line:tst-imp-start}{line:tst-imp-end} implement the system using the component (\lineref{line:tst-imp-comp})

@@

>>>>

Unit tests are created in AGREE by writing a system specification that assumes the test input and then guarantees the test output.
The system is then implemented with the component under test and its specification.
The AGREE analysis then proves if the component guarantees, given the test inputs, are strong enough to prove the guaranteed test outputs.
Here the system assumptions strengthen the component assumptions to a single input, and the system guarantees weaken, or leave unchanged, the component output for that test input, depending on the goal of the test.
AGREE proves the component implements the test, and the Liskov substitution principle holds.

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{c}
    \scalebox{0.62}{\usebox{\tst}} \\
    \end{tabular}
  \end{center}
  \caption{AGREE unit test for high-assurance monitor.}
  \label{fig:test}
\end{figure}

\figref{fig:test} is a unit test for the high-assurance monitor in \figref{fig:hardened}.
The test checks if the monitor output coincides with the response that comes one step after the request.
It also checks that the alarm does not fire.
\lineref{line:tst-index} creates an index to use to create the test input.
\lineref{line:tst-assume-1} defines when the response appears relative to the index.
\lineref{line:tst-assume-2} defines the request behavior.
\linesref{line:tst-guarantee-1}{line:tst-guarantee-2} define the expected test output.
The test additionally proves that nothing happens after the initial test input and output (e.g., no more input is provided and no more output is generated).
AGREE proves the test correct.
\linesref{line:tst-imp-start}{line:tst-imp-end} implement the system using the component (\lineref{line:tst-imp-comp}).
\figref{fig:test-output} is the AGREE output for the test is showing that it passes.

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{c}
      \includegraphics[scale=0.38]{agree-test-output.png} \\
    \end{tabular}
  \end{center}
  \caption{AGREE output for unit test.} 
  \label{fig:test-output}
\end{figure}
